$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-03-27 paper/e6ssm-tuning-paper.tex
small rephrasing for clarity.

Here we will refer to U(1) extensions of the MSSM, which solve the
$\mu$-problem, as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
  Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}.  The couplings for the
$U(1)^\prime$ gauge group should allow the following renormalisable
superpotential terms required in the USSM, \begin{equation}
 W_{USSM} = y^U_{ij}
\hat{u}^c_i  \hat{H}_u \cdot \hat{Q}_j + y^D_{ij} \hat{d}^c_i  \hat{Q}_j \cdot \hat{H}_d
 + y^E_{ij} \hat{e}^c_i \hat{L}_j \cdot \hat{H}_d  + \lambda \hat{S} \hat{H}_d \cdot \hat{H}_u, 
\end{equation} with $i,j \in \{1,2,3\}$. 
For the $SU(2)$ dot product we follow the convention $\hat{A}\cdot \hat{B}\equiv \epsilon_{\alpha\beta}\hat{A}^\alpha\hat{B}^\beta=\hat{A}^2\hat{B}^1-\hat{A}^1\hat{B}^2$.

@@

The breaking of $E_6$ into $SO(10)$, gives rise to $E_6\to
SO(10)\times U(1)_{\psi}$, and the subsequent breaking of $SO(10)$
into $SU(5)$, gives $SO(10)\to SU(5)\times U(1)_{\chi}$ (this is
reviewed in e.g.~\cite{Langacker:2008yv}). The extra $U(1)$ gauge
symmetry at low energies should then be a linear combination of these
in the $E_6$ inspired case, \be U(1)^\prime = U(1)_{\chi}\cos\theta 
+ U(1)_{\psi}\sin\theta . \ee In Table \ref{tab:E6charges} the
charges for several popular $E_6$ inspired $U(1)$ extensions are
shown.
% Table of U(1)' charges, which may or may not be useful to include.
\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cccccccccccccc}
 & $\hat{Q}$ & $\hat{u}^C$ & $\hat{d}^C$ & $\hat{L}$ & $\hat{e}^C$ & $\hat{N}^C$ & $\hat{S}$ & $\hat{H}_2$ & $\hat{H}_1$ & $\hat{D}$ & $\hat{\overline{D}}$ & $\hat{H}'$ & $\hat{\overline{H'}}$ \\[1mm]
\hline
$\sqrt{\frac{5}{3}}Q_i^Y$ & $\frac{1}{6}$ & $-\frac{2}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $1$ & $0$ & $0$ & $\frac{1}{2}$ & $-\frac{1}{2}$ & $-\frac{1}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $\frac{1}{2}$ \\[1mm]
%\hline
$2\sqrt{6}Q_i^\psi$ & $1$ & $1$ & $1$ & $1$ & $1$ & $1$ & $4$ & $-2$ & $-2$ & $-2$ & $-2$ & $1$ & $-1$\\[1mm]
%\hline
$2\sqrt{10}Q_i^\chi$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-5$ & $0$ & $2$ & $-2$ & $2$ & $-2$ & $3$ & $-3$\\[1mm]
%\hline
$\sqrt{40}Q_i^N$ & $1$ & $1$ & $2$ & $2$ & $1$ & $0$ & $5$ & $-2$ & $-3$ & $-2$ & $-3$ & $2$ & $-2$ \\[1mm]
\end{tabular}
\end{ruledtabular}
\caption{The $U(1)_Y$, $U(1)_\psi$, $U(1)_\chi$ and $U(1)_N$ charges of the chiral superfields in the $E_6$ model. The specific case of $U(1)_N$, corresponding to the E$_6$SSM, is obtained for $\theta=\arctan\sqrt{15}$.}
\label{tab:E6charges}
\end{table}

@@

\be
W_{E_6} = W_0 + W_1 + W_2,
\label{Eq:e6-superpot}
\ee where
\begin{eqnarray}
W_0 &=& \lambda_{ijk} \hat{S}_i  \hat{H}^d_{j} \cdot\hat{H}^u_{k} + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i  \hat{H}^u_{j} \cdot \hat{L}_k \nonumber \\
& & + h^U_{ijk} \hat{u}^c_i  \hat{H}^u_{j} \cdot \hat{Q}_k + h^D_{ijk} \hat{d}^c_i  \hat{Q}_k\cdot\hat{H}^d_{j}  + h^E_{ijk} \hat{e}^c_i  \hat{L}_k\cdot\hat{H}^d_{j} , \\
W_1 &=& g^Q_{ijk} \hat{D}_i  \hat{Q}_j \cdot \hat{Q}_k + g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk}  \hat{Q}_i \cdot \hat{L}_j \hat{\bar{D}}_k.
\label{Eq:e6-superpot-parts}
\end{eqnarray}

Nonetheless while this model is very elegant so far, the
superpotential of Eq.~(\ref{Eq:e6-superpot}) contains dangerous terms which
can induce proton decay and lead to large flavour changing neutral
currents (FCNCs).  There are a number of approaches to suppress these
terms, involving the use of different discrete symmetries.  Here for
the purposes of renormalisation group running we will simply include
the following unsuppressed superpotential terms, which follows the
approach taken in work on the cE$_6$SSM \cite{Athron:2009ue,
  Athron:2009bs},
%
%% \begin{align}
%%   \begin{split}
    \ba
    W &\approx& y_{\tau} \SuperField{L}_3 \cdot \SuperField{H}_d
      \SuperField{e}^C_3 + y_b \SuperField{Q}_3\cdot\SuperField{H}_d
      \SuperField{d}_3^C + y_t \SuperField{H}_u\cdot\SuperField{Q}_3
      \SuperField{u}_3^C\\
    &&
    + \lambda_i \SuperField{S} \SuperField{H}_{1i}
    \cdot \SuperField{H}_{2i}  + \kappa_i \SuperField{S} \SuperField{D}_i
    \SuperField{\overline{D}}_i + \mu' \SuperField{H}'\cdot
    \SuperField{\overline{H'}},
    \ea
  %% \end{split}
  \label{SuPot_RGE}
%%\end{align}
%

@@

V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|H_1\cdot
H_2|^2,\label{eq:E6VFterms}\\ 
V_D&=\frac{\bar{g}^2}{8}\left (

@@

H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ 
V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
[\lambda A_\lambda SH_1\cdot H_2+\textrm{h.c.}\Big

@@

$H_1$, $H_2$ and $S$, respectively. In the case

@@

$\mu$ term, as occurs in the MSSM. The term $\Delta V$ contains the
Coleman-Weinberg contributions to the effective potential. For the purposes of this study, 
we include in $\Delta V$ only the one-loop contributions from the top quark and stop squarks,
\Delta V=\frac{3}{32\pi^2}\left [ m_{\tilde{t}_1}^4\left ( \log\frac{m_{\tilde{t}_1}^2}{Q^2}-\frac{3}{2}\right )+m_{\tilde{t}_2}^4\left ( \log\frac{m_{\tilde{t}_2}^2}{Q^2}-\frac{3}{2}\right )-2m_t^4\left ( \log\frac{m_t^2}{Q^2}-\frac{3}{2}\right )\right ].
Explicit expressions for the running $\overline{\textrm{DR}}$ top mass $m_t$ and stop masses $m_{\tilde{t}_{1,2}}$ are given 
below.\\
Demanding that the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of the form

@@

(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\

@@

(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V}{\partial s}=0.\label{eq:E6EWSBcondition3}

@@

D_\phi\equiv \frac{g_1'^2}{2}\left (Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right )Q_\phi.
We also include these $U(1)'$ $D$-term contributions in the diagonalised stop masses,
  m_{\tilde{t}_{1,2}}^2&=\frac{1}{2}\bigg \{ m_{Q3}^2+m_{u3}^2+\frac{1}{2}M_Z^2\cos 2\beta+D_Q+D_u+2m_t^2\nonumber\\
&\quad{}\mp\sqrt{\left [ m_{Q3}^2+m_{u3}^2+\left ( \frac{1}{2}-\frac{4}{3}\sin^2\theta_W\right )M_Z^2\cos 2\beta + D_Q-D_u\right ]^2+4m_t^2X_t^2}\bigg \},
where $m_t^2=y_t^2v_2^2/2$ and $X_t=A_t-\frac{\lambda s v_1}{\sqrt{2}v_2}$. By definition we take $m_{\tilde{t}_1}$ to correspond to the lighter of the two states.\\
As was noted in \cite{Athron:2013ipa}, the first two of these conditions may be rewritten in the form

@@

Written in the form of Eq.~(\ref{eq:E6MZequation}) we see the

@@

right-hand side of Eq.~(\ref{eq:E6MZequation}) must be tuned to cancel

@@

can be made even clearer by writing Eq.~(\ref{eq:E6MZequation}) in the

@@

@@

Eq.~(\ref{eq:E6masterformula}).\\
However, it is well known in the

@@

Eq.~(\ref{eq:E6EWSBConditions}), rather than
Eq.~(\ref{eq:E6MZequation}). The general procedure that we use is as follows
(this method has also previously been applied in the NMSSM, see for example \cite{Ellwanger:2011mu}). For a model in which $m$ fields develop real

@@

with $M_h^2$, are easily calculated by differentiating the conditions in Eq.~(\ref{eq:E6EWSBConditions})
with respect to the VEVs and the running parameters. 
The remaining derivatives $\partial q_k /\partial p$ must be determined using the

@@

v_i/\partial p$ and $\partial q_k/\partial p$. The effects of radiative corrections
may be easily included by including the Coleman-Weinberg potential
contributions $\Delta V$ in the EWSB conditions.\\
Evaluating the derivatives

@@

\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band). Note that there are points for which
the fine tuning in the MSSM and E$_6$SSM with $M_{Z'}=2.5$ TeV is larger than is visible on this plot
and those below;
however these points are obscured by the overlaid data for the E$_6$SSM with $M_{Z'}=4.5$ TeV, and it is the 
lower bound on the achievable tuning that is of interest here.}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we
find that, for the points satisfying the current limit on the mass of
the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
minimum fine tuning that can be achieved is
$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
the fine tuning in the model will be greater than at least
$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
GeV and $125.5$ GeV.

@@

As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the tunings varies quite
a bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These charges change the
value of the coefficient $d$ in Eq.~(\ref{eq:originalE6MZequation}).
The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
U(1)_\eta \}$ and this determines which of the models are most tuned.

@@

with $f_1,f_2,f_3$ as given in Eq.~(\ref{eq:E6EWSBConditions}). The relevant partial derivatives are

@@

It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}). Similarly, the quantity $C$ appearing in Eq.~(\ref{eq:E6masterformula}) is given by

@@

approximated by a Taylor series, Eq.~(\ref{eq:rgeapproxsoln}).  For a

@@

diagonal, and the gaugino masses are taken to be real.\\
In the

@@

with \footnote{The first of these is the trace which is assumed to vanish in

@@

  gauge kinetic mixing this is done in SARAH by removing the RGE for

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [Q_1^2+Q_2^2+\left ( Q_2 - Q_1 \right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\

@@

\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i^2\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\

@@

&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2+\left ( 3Q_2+Q_Q-4Q_u\right )\Sigma_Q^Y\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\

>>>>

Here we will refer to U(1) extensions of the MSSM, which solve the
$\mu$-problem, as the USSM \cite{Cvetic:1995rj, Jain:1995cb,
  Nir:1995bu, Cvetic:1996mf, Cvetic:1997ky}.  The couplings for the
$U(1)^\prime$ gauge group should allow the following renormalisable
superpotential terms required in the USSM, \be W_{USSM} = y^U_{ij}
\hat{u}^c_i \left ( \hat{H}_u \cdot \hat{Q}_j \right ) + y^D_{ij} \hat{d}^c_i 
\left ( \hat{Q}_j \cdot \hat{H}_d \right )
 + y^E_{ij} \hat{e}^c_i \left ( \hat{L}_j \cdot \hat{H}_d \right ) + \lambda \hat{S}
\left ( \hat{H}_d \cdot \hat{H}_u \right ), \ee with $i,j \in \{1,2,3\}$. 
For the $SU(2)$ dot product we follow the convention $\hat{A}\cdot \hat{B}\equiv \epsilon_{\alpha\beta}\hat{A}^\alpha\hat{B}^\beta=\hat{A}^2\hat{B}^1-\hat{A}^1\hat{B}^2$.

@@

The breaking of $E_6$ into $SO(10)$, gives rise to $E_6\to
SO(10)\times U(1)_{\psi}$, and the subsequent breaking of $SO(10)$
into $SU(5)$, gives $SO(10)\to SU(5)\times U(1)_{\chi}$ (this is
reviewed in e.g.~\cite{Langacker:2008yv}). The extra $U(1)$ gauge
symmetry at low energies should then be a linear combination of these
in the $E_6$ inspired case, \be U(1)^\prime = \cos(\theta) U(1)_{\chi}
+ \sin(\theta) U(1)_{\psi}. \ee In Table \ref{tab:E6charges} the
charges for several popular $E_6$ inspired $U(1)$ extensions are
shown.
% Table of U(1)' charges, which may or may not be useful to include.
\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cccccccccccccc}
 & $\hat{Q}$ & $\hat{u}^C$ & $\hat{d}^C$ & $\hat{L}$ & $\hat{e}^C$ & $\hat{N}^C$ & $\hat{S}$ & $\hat{H}_2$ & $\hat{H}_1$ & $\hat{D}$ & $\hat{\overline{D}}$ & $\hat{H}'$ & $\hat{\overline{H'}}$ \\[1mm]
\hline
$\sqrt{\frac{5}{3}}Q_i^Y$ & $\frac{1}{6}$ & $-\frac{2}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $1$ & $0$ & $0$ & $\frac{1}{2}$ & $-\frac{1}{2}$ & $-\frac{1}{3}$ & $\frac{1}{3}$ & $-\frac{1}{2}$ & $\frac{1}{2}$ \\[1mm]
%\hline
$2\sqrt{6}Q_i^\psi$ & $1$ & $1$ & $1$ & $1$ & $1$ & $1$ & $4$ & $-2$ & $-2$ & $-2$ & $-2$ & $1$ & $-1$\\[1mm]
%\hline
$2\sqrt{10}Q_i^\chi$ & $-1$ & $-1$ & $3$ & $3$ & $-1$ & $-5$ & $0$ & $2$ & $-2$ & $2$ & $-2$ & $3$ & $-3$\\[1mm]
%\hline
$\sqrt{40}Q_i^N$ & $1$ & $1$ & $2$ & $2$ & $1$ & $0$ & $5$ & $-2$ & $-3$ & $-2$ & $-3$ & $2$ & $-2$ \\[1mm]
\end{tabular}
\end{ruledtabular}
\caption{The $U(1)_Y$, $U(1)_\psi$, $U(1)_\chi$ and $U(1)_N$ charges of the chiral superfields in the $E_6$ model. The specific case of $U(1)_N$, corresponding to the E$_6$SSM, is obtained for $\theta=\arctan\sqrt{15}$.}
\label{tab:E6charges}
\end{table}

@@

\be
W_{E_6} = W_0 + W_1 + W_2,
\label{Eq:e6-superpot}
\ee where
\begin{eqnarray}
W_0 &=& \lambda_{ijk} \hat{S}_i \left ( \hat{H}^d_{j} \cdot\hat{H}^u_{k}\right ) + \kappa_{ijk} \hat{S}_i \hat{D}_j \hat{\bar{D}}_k + h^N_{ijk} \hat{N}^c_i \left ( \hat{H}^u_{j} \cdot \hat{L}_k\right ) \nonumber \\
& & + h^U_{ijk} \hat{u}^c_i \left ( \hat{H}^u_{j} \cdot \hat{Q}_k\right ) + h^D_{ijk} \hat{d}^c_i \left ( \hat{Q}_k\cdot\hat{H}^d_{j}\right )  + h^E_{ijk} \hat{e}^c_i \left ( \hat{L}_k\cdot\hat{H}^d_{j}\right ) , \\
W_1 &=& g^Q_{ijk} \hat{D}_i \left ( \hat{Q}_j \cdot \hat{Q}_k \right )+ g^q_{ijk} \hat{\bar{D}}_i \hat{d}^c_j \hat{u}^c_k, \\
W_2 &=& g^N_{ijk} \hat{N}^c_i \hat{D}_j \hat{d}^c_k + g^E_{ijk} \hat{e}^c_i \hat{D}_j \hat{u}^c_k + g^D_{ijk} \left ( \hat{Q}_i \cdot \hat{L}_j \right )\hat{\bar{D}}_k.
\label{Eq:e6-superpot-parts}
\end{eqnarray}

Nonetheless while this model is very elegant so far, the
superpotential of Eq.~(\ref{Eq:e6-superpot}) contains dangerous terms which
can induce proton decay and lead to large flavour changing neutral
currents (FCNCs).  There are a number of approaches to suppress these
terms, involving the use of different discrete symmetries.  Here for
the purposes of renormalisation group running we will simply include
the following unsuppressed superpotential terms, which follows the
approach taken in work on the cE$_6$SSM \cite{Athron:2009ue,
  Athron:2009bs},
%
%% \begin{align}
%%   \begin{split}
    \ba
    W &\approx& y_{\tau} \left (\SuperField{L}_3 \cdot \SuperField{H}_d
     \right ) \SuperField{e}^C_3 + y_b \left (\SuperField{Q}_3\cdot\SuperField{H}_d
     \right ) \SuperField{d}_3^C + y_t \left (\SuperField{H}_u\cdot\SuperField{Q}_3
     \right ) \SuperField{u}_3^C\\
    &&
    + \lambda_i \SuperField{S} \left (\SuperField{H}_{1i}
    \cdot \SuperField{H}_{2i} \right ) + \kappa_i \SuperField{S} \SuperField{D}_i
    \SuperField{\overline{D}}_i + \mu' \left (\SuperField{H}'\cdot
    \SuperField{\overline{H'}}\right ),
    \ea
  %% \end{split}
  \label{SuPot_RGE}
%%\end{align}
%

@@

V_F&=\lambda^2|S|^2(|H_1|^2+|H_2|^2)+\lambda^2|(H_1\cdot
H_2)|^2,\label{eq:E6VFterms}\\ V_D&=\frac{\bar{g}^2}{8}\left (

@@

H_2|^2+\frac{g_1'^2}{2}(Q_1|H_1|^2+Q_2|H_2|^2+Q_S|S|^2)^2,\label{eq:E6VDterms}\\ V_{\textrm{soft}}&=m_S^2|S|^2+m_{H_d}^2|H_1|^2+m_{H_u}^2|H_2|^2+\Big
[\lambda A_\lambda S(H_1\cdot H_2)+\textrm{h.c.}\Big

@@

$H_1$, $H_2$ and $S$, respectively. The term $\Delta V$ contains the
Coleman-Weinberg contributions to the effective potential. In the case

@@

$\mu$ term, as occurs in the MSSM.\\ \\ Demanding that
the Higgs fields $H_1$, $H_2$ and the singlet $S$ acquire real VEVs of
the form

@@

(v_2^2-v_1^2)v_1+D_{H_1}v_1+\frac{\partial \Delta V_{E_6}}{\partial v_1}=0,\label{eq:E6EWSBcondition1} \\

@@

(v_2^2-v_1^2)v_2+D_{H_2}v_2+\frac{\partial \Delta V_{E_6}}{\partial v_2}=0,\label{eq:E6EWSBcondition2} \\
&f_3=m_S^2s+\frac{\lambda^2}{2}(v_2^2+v_1^2)s-\frac{\lambda A_\lambda}{\sqrt{2}}v_2v_1+D_Ss+\frac{\partial \Delta V_{E_6}}{\partial s}=0.\label{eq:E6EWSBcondition3}

@@

D_\phi\equiv \frac{g_1'^2}{2}\left (
Q_1v_1^2+Q_2v_2^2+Q_Ss^2\right
)Q_\phi.
As was noted in \cite{Athron:2013ipa}, the first two of these
conditions may be rewritten in the form

@@

Written in the form of Eq. (\ref{eq:E6MZequation}) we see the

@@

right-hand side of Eq. (\ref{eq:E6MZequation}) must be tuned to cancel

@@

can be made even clearer by writing Eq. (\ref{eq:E6MZequation}) in the

@@

%% \section{\label{sec:tuning}Fine Tuning}
% Introduce tuning measure - BG measure (maybe Peter will add in a justification
% here).
% Explain that we derived the master formula in the E6SSM as given in Maien's 
% paper, but including extra effects not in that formula. 
% Full result is given in appendix.
% Numerical technique for calculating 1-loop tunings and including RG effects
% Outline is given here, full equations for RGE effects etc. given in appendix.
% How we calculate the tuning using spectrum generator, for E6SSM uses
% FlexibleSUSY (cite FlexibleSUSY and SARAH).

@@

Eq. (\ref{eq:E6masterformula}).\\ \\ However, it is well known in the

@@

Eq. (\ref{eq:E6EWSBConditions}), rather than
Eq. (\ref{eq:E6MZequation}). The general procedure is as follows
\cite{Ellwanger:2011mu}. For a model in which $m$ fields develop real

@@

with $M_h^2$, are easily calculated analytically. The remaining
derivatives $\partial q_k /\partial p$ must be determined using the

@@

v_i/\partial p$ and $\partial q_k/\partial p$. Radiative corrections
may be easily incorporated by including the Coleman-Weinberg potential
contributions in the EWSB conditions.\\ \\ Evaluating the derivatives

@@

%   Since the stop mass does not have a large impact on the fine tuning
%   when the cutoff scale is very low we can use this to see more clearly
%   the impact of the $Z^\prime$ mass on fine tuning. To do se we choose a
%   cutoff of  look at the fine tuning for two different
%   values of the $Z^\prime$ mass, $2.5$ TeV, which is just above the
%   current limits and $4.5$ TeV which could be in reach of the LHC run
%   II, and compare these to the MSSM.

%   For this we also fix [what we fix + explain different choices to
%   before and their impact].
\begin{figure}[h]
\begin{center}
\resizebox{!}{10cm}{%
\includegraphics{all_models_tuning_vs_higgs.png}}
\caption{Scatter plot of fine tuning vs lightest Higgs mass for the
  MSSM (green, bottom band), E$_6$SSM with $M_{Z^\prime} = 2.5$ TeV (blue, middle band) and
  E$_6$SSM with $M_{Z^\prime} = 4.5$ TeV (red, top band).}
\label{Fig:e6ssmvsmssm}
\end{center}
\end{figure}
In Fig \ref{Fig:e6ssmvsmssm} results from the scan are plotted showing
the tuning for each case against the lightest Higgs mass.  As expected
the dependence on the Higgs mass is now quite weak, while the minimum
tuning in the model for the E$_6$SSM is increased by the mass of the
$Z^\prime$ boson.  So in the case of a very low cutoff the tuning
required to get a 125 GeV Higgs is not so large.  However the tuning
from the $Z^\prime$ mass appears already at tree level and is
therefore not suppressed when the cutoff scale is low. In our scan we
find that, for the points satisfying the current limit on the mass of
the $Z^\prime$ boson and having an approximately 125 GeV Higgs, the
minimum fine tuning that can be achieved is
$\Delta_{\textrm{min}}\approx 121$. If run II of the LHC further
pushes up the limit on the $Z^\prime$ mass to be above $4.5$ TeV then
the fine tuning in the model will be greater than at least
$\Delta_{\textrm{min}}\approx 394$ for a Higgs mass between $124.5$
GeV and $125.5$ GeV.

@@

As can be seen in Fig.~\ref{Fig:othere6modelsvsmssm} the severity of the tunings varies quite
a bit.  This is because the charges appear as coefficients in front of
the $Z^\prime$ mass in the EWSB condition.  These charges change the
value of the coefficient $d$ in Eq. (\ref{eq:originalE6MZequation}).
The values of the coefficient $d$ in each model, for $\tan\beta = 10$,
is $\{-0.01, 0.40, 0.50, 0.81 \}$ for $\{U(1)_I, U(1)_N, U(1)_\psi,
U(1)_\eta \}$ and this determines which of the models are most tuned.

@@

with $f_1,f_2,f_3$ as given in Eq. (\ref{eq:E6EWSBConditions}). The relevant partial derivatives are

@@

It is straightforward to compute the appropriate derivatives directly from the EWSB conditions (\ref{eq:E6EWSBConditions}). Similarly, the quantity $C$ appearing in Eq. (\ref{eq:E6masterformula}) is given by

@@

approximated by a Taylor series, Eq. (\ref{eq:rgeapproxsoln}).  For a

@@

diagonal, and the gaugino masses are taken to be real.\\ \\ In the

@@

with \footnote{This is the trace which is assumed to vanish in

@@

  gauge kinetic mixing, SARAH does this by removing the RGE for

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( Q_1^2+Q_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left (Q_1^2+Q_2^2\right )\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\

@@

\beta_{m_S^2}^{(1)}&=\sum_{i=1}^3\left [ 4\lambda_i^2\left ( m_{H_i^d}^2+m_{H_i^u}^2+m_S^2\right )+4a_{\lambda_i}^2+6\kappa_i\left ( m_S^2+m_{D_i}^2+m_{\overline{D}_i}^2\right )+6a_{\kappa_i}^2\right ]\nonumber\\

@@

&{}+\frac{2}{5}g_1^2g_1'^2\left [ 3Q_2^2+\frac{1}{3}Q_Q^2+\frac{16}{3}Q_u^2\right ]\bigg \},\label{eq:USSMYu22BetaTwoLoop}\\
